\problemname{Darts Scoring}
\illustration{0.4}{board}{Image taken from \href{https://commons.wikimedia.org/wiki/File:Darts\_in\_board.png}{commons.wikimedia.org}}

Hannes went to a work gathering with his coworkers and like many times before the choice of venue
was a darts bar, as is very common with Icelandic software development companies. As the game progressed
it became clear to Hannes that one of the other players was very likely to finish the game on
his next round. Thus he figures he has to finish the game right now on his round to win. 
But how can he go about this?

In each round a player can throw up to three darts. For hitting directly in the centre you
get $50$ points, this is called a \texttt{Bullseye}. For hitting the ring around the centre you
get $25$ points, this is called a \texttt{Outer bullseye}. Then there are $20$ slices of
the circle outside this centre. Hitting a given slice gives $1$ to $20$ points depending on
the slice, so hitting slice $17$ would for example give $17$ points and be called 
\texttt{Single 17}. On each slice is a narrow strip that gives double points, so hitting
that strip on slice $8$ would give $16$ points and be called \texttt{Double 8}. Finally
there is another narrow strip on each slice that gives triple points, so hitting that strip
on slice $11$ would give $33$ points and be called a \texttt{Triple 11}.

Can you tell Hannes all the ways he could finish the game in at most three throws?

Note that you do not have to end with a specific kind of throw like \texttt{Double} unlike in
some versions of darts.

\section*{Input}
The input contains a single positive integer $x$, the number of points Hannes needs to score to
finish the game. It will always hold that $x \leq 501$.

\section*{Output}
You should start by printing a single line with an integer $n$ that gives the number of ways
that Hannes can finish the game on his round in one to three throws. For each such way you
should print the following. First print an integer $k$ on its own line, the number of throws
to be made. Then there should follow $k$ lines, the $i$-th of which gives where the $i$-th dart
should land, using the names given above.

Notice that \texttt{Bullseye}, \texttt{Single 1} and \texttt{Single 1}, \texttt{Bullseye} count as
different ways to get $51$ points, the order does not matter.

However, the order in which the ways to get $x$ points are printed does not matter. Any ordering is considered correct.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $x = 1$. \\ \hline
2     & 30   & $x \leq 5$. \\ \hline
3     & 40   & $x \leq 100$. \\ \hline
4     & 10   & No further constraints. \\ \hline
\end{tabular}

