\problemname{Skattmann}
\illustration{0.3}{taxmanimg}{Image taken from \href{https://commons.wikimedia.org/wiki/File:RISD_Tax_Collectors.jpg}{commons.wikimedia.org}}

You just got paid, all numbers from $1$ to $n$ are now in your possession after
a hard month. But unfortunately things aren't quite so simple, because now you
have to pay tax. You sit down across from the Skattmann, and the game begins. You
may take one of the numbers from $1$ to $n$ to keep. If you take the number $m$
the Skattmann takes all numbers $d$ that divide $m$, and if there is no such number
$d$ you aren't allowed to take $m$ since everything has to be taxed. For example
you are not allowed to start by taking $1$. At the end the Skattmann takes all remaining
numbers.

Your goal is to pay the minimum tax possible, at least strictly less than $50\%$.
For example if $n = 13$ we can start by taking $13$ and the Skattmann takes $1$. If
we then take $9$ the Skattmann takes $3$. Next we could take $10$ and then the Skattmann
takes both $2$ and $5$. If we then take $8$ the Skattmann takes $4$. Finally if we
take $12$ the Skattmann takes $6$, and then both $7$ and $11$ because we can't take
either of them so the game is over. In total we get $52$ and the Skattmann gets $39$,
so we got more than half.

\section*{Input}
The input contains a single integer $4 \leq n \leq 10\,000$.

\section*{Output}
First print the number of numbers you intend to take on its own line. On the next line print
the numbers you intend to take, in the order you intend to take them, with a single space
between numbers.

\section*{Scoring}
The solution will be run on $100$ different test cases. If if the solution returns
an invalid answer, no points are given. If the judge solution gets $s$ and you get $x$
you get $(4x - n(n + 1)) / (4s - n(n + 1))$ points for that test case, at least $0$ points
and at most $1$ points though. This means that if you pay $50\%$ tax you get $0$ points, increasing
linearly to $1$ point as you get closer to the judge solution.

The test cases are divided into two $50$ test groups, one has $n \leq 1\,000$ and the other
has $1\,000 < n \leq 10\,000$.
