\problemname{Flýtibaka}
\illustration{0.3}{fastpizza}{Photo from \href{https://www.flickr.com/photos/memnativ/5393520746}{flickr.com}}

Ómar is ordering pizza for his family.
He is very lazy and therefore wants to minimize the time and effort put into ordering the pizza.
He doesn't care what toppings go on the pizza as long as the basics are there: bread, cheese and sauce.
Luckily there is a service which suits Ómar perfectly.

The company Flýtibaka provides a service for people that want their pizza quickly.
A website, app or phone call is not used to make an order at Flýtibaka.
It is instead sufficient to text their phone number with a message which includes all the toppings desired by the customer on the pizza.
Unless otherwise specified in the order, the pizzas will be made with regular dough and topped with cheese and sauce.
It is unnecessary to include more info in the order as Flýtibaka has collected data on the locations and appetites of everyone in the world.
That is how the company can determine the size of the order and where to deliver it.

Now it is time to make the order and Ómar cannot be bothered to write a long list of ingredients.
He just wants to send as short of a text as he possibly can, while still being happy with the food.
What should Ómar send?

\section*{Input}
There is no input in this task.

\section*{Output}
Output the text that Ómar should write in his text message.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 100    & No further constraints\\ \hline
\end{tabular}

