\problemname{Láki}
\illustration{0.4}{laki}{Image taken from the book Láki.}

The other year there was a problem on this contest called Leggja Saman.
In that problem there were two numbers in the input and the problem
was to add them together. The plan was to have a similar problem on
the contest this year, but there was a bit of an incident when the
problem was copied over. Láki managed to get into the computer system
of the Competitive Programming Society of Iceland! If only Arnar had
managed to upgrade his computer before the contest.

The result is that Láki managed to change the input data in the problem
to fit with his ideas of addition. He very much likes to immiserate other
people, so the input data is sure to contain all kinds of strange and
tedious kinds of addition. The only thing that the society can deduce
is that the input data is split into $10$ locked folders, each marked
with $10$ points. So there should be $10$ kinds of strange addition
in the input data.

Luckily the people at Kattis have some ability to help here! Thanks to
their intervention you should be able to see exactly what goes wrong in
your submission after you submit, and thus be able to deduce what additions
Láki has put in the input data!

\section*{Input}
The input contains a single line of the form \texttt{x + y}.
However, we don't exactly know what \texttt{x} or \texttt{y} will be!

\section*{Output}
Print the sum of \texttt{x} and \texttt{y}, however Láki defines it!

\section*{Scoring}
There are $10$ folders, so $10$ points are given for each type of
addition the program manages to do as Láki defines it.

