\problemname{Ferskasta Jarmið}
\illustration{0.5}{fellow}{Image taken from \href{https://www.deviantart.com/adiyah/art/Learning-English-Slang-With-Aruran-Papa-865652411}{deviantart.com}}

Bjarki worries a lot about his social media performance. He cares deeply about being hip and cool in the eyes of the current youth.
After much research and extensive measurements, he has determined two main factors deciding how much attention a given meme will get
on social media. Controversiality, how controversial the meme is, decides how many seconds the meme will stay in circulation on the users'
procedurally generated custom feeds. Coolness, how cool the meme is, will determine how much attention the meme gets per second. In total,
this determines how fresh the meme is, that is to say how much attention it receives in total before being banished to the dark depths
of the world wide web.

He has collected a shortlist of prospective memes he could put on his social media. Can you determine which of them is freshest so he
chooses the correct meme?

\section*{Input}
The first line of input contains a single integer $1 \leq n \leq 100$, the number of memes Bjarki put on the shortlist.
The next $n$ lines contain one meme each. Each line contains the name of the meme, the controversiality and the coolness. The
controversiality and coolness are integers from $0$ to $100$, both ends being inclusive. The name contains only English upper and lower case characters along with
dots, underscores and digits. The names are of length at most $50$. No name will appear more than once.

\section*{Output}
Print the name of the freshest meme. If many memes are equally fresh, print the one that comes first by alphabetical order.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 50   & No memes are equally fresh. \\ \hline
2     & 50   & No further constraints. \\ \hline
\end{tabular}
