\problemname{Ævintýraröð}
\illustration{0.4}{scroll}{Image taken from \href{https://commons.wikimedia.org/wiki/File:Noun_Scroll_308110.svg}{commons.wikimedia.org}}

Jörmunrekur was looking into his old favourite video game called DeceitfulLOAM and discovered that not only was it considered ancient
history, but there had been three new versions of it since he played it, two of which are also considered ancient as well, and one of which had even
risen from the dead! He will accept some changes when moving up to new versions, but there are limits to everything. He decides to play
the version that comes after DeceitfulLOAM, known as Glyphplane Classic. He reads a bit about the changes and finds out that in this
version various quests have been added which increase a player's experience points upon completion. Learning this makes his mind
start grinding away.

The rewards scale with the player's current experience points. More specifically, each quest has some values $a$ and $b$ such that
if the player currently has $x$ experience points, the quest reward will be $ax + b$ more experience points. 
This means they have $x + ax + b$ experience points after the quest.
Naturally, Jörmunrekur wants to increase these values as efficiently as possible, so in what order should he complete the quests?

\section*{Input}
The first line of input contains two integers $n$ and $x$, the number of quests and Jörmunrekur's initial number of
experience points, where $0 \leq x \leq 1\,000$. Next there are $n$ lines, each describing one quest. Each line starts with the name of the quest, followed by its
values of $a$ and $b$, where $0 \leq a, b \leq 1\,000$, all separated by spaces. The names only contain English upper and lower case letters and are at most
$20$ characters in length. The total length of all names in the input is at most $300\,000$. All quests have different names.

\section*{Output}
Print the names of the quests in the order Jörmunrekur should finish them, meaning the quest he should complete first should be
printed first. Print each name on its own line. If there are multiple correct answers, you may print any one of them.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $1 \leq n \leq 2$ \\ \hline
2     & 20   & $1 \leq n \leq 8$ \\ \hline
3     & 20   & $1 \leq n \leq 50$ \\ \hline
4     & 20   & $1 \leq n \leq 500$ \\ \hline
5     & 20   & $1 \leq n \leq 10^5$ \\ \hline
\end{tabular}

