\problemname{Maximally Unfair Fair IKEA Trip}
\illustration{0.4}{ikealogo}{Image from \href{https://commons.wikimedia.org/wiki/File:Ikea\_logo.svg}{Wikimedia.org}}

Dagur and his friends were in IKEA buying furniture for the Faulty Komputerprogram (FK) club, but Dagur is lazy and does not want to carry furniture all the way back.
But everyone has to carry the same number of items, otherwise it would be unfair. Therefore, Dagur has decided to carry as little weight as possible.

You are given $k$, the number of people carrying stuff (Dagur and his friends), and a list of $n$ furniture items and their weights.
Find what items Dagur should carry to minimise weight.

Note that the number of people does not necessarily divide 
the number of goods, so not everyone can carry the same
number of items. If this is the case Dagur will try to take
as few items as possible, as long as it does not make it too
obvious he's trying to get away lightly. 

Dagur will try to get away with taking only $\lfloor n/k
\rfloor$ items. The only exception is when this would make
his laziness obvious. This happens when the lightest 
$\lceil n/k \rceil$ items are strictly lighter than the next 
$\lfloor n/k \rfloor$ items, when they are ordered by weight.
In this case Dagur will take $\lceil n/k \rceil$ items to
make things less obvious.

Let us take an example with $7$ items and $3$ people carrying, that is to say $n = 7$ and
$k = 3$. Call the items $x_1, x_2, \ldots, x_{7}$ after putting them in increasing weight order,
so $x_1 < x_2 < \cdots < x_{7}$. Then Dagur will take $2$ items, unless if
$x_1 + x_2 + x_3 < x_4 + x_5$, then he will take $3$ items instead.

If there are multiple different lightest sets of items that 
Dagur can take, Dagur breaks ties by taking the items that
appeared earliest in the list of bought items.

\section*{Input}
Input consists of multiple lines.
The first line contains a single integer $k$, the number of people carrying items.
The next line contains a single integer $n$, the number of products purchased at IKEA\@.
The next line contains $n$ lines, the list of all bought products, each line containing the name of one product and its weight. Each weight is at most $100\,000$.
Each name is at most 10 English letters and has no spaces, names are also not empty.

\section*{Output}
On the first line, write the total weight that Dagur carries on his shoulders.
The next lines should contain all the items that Dagur carries on his shoulders in alphabetical order, one per line.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Groups & Points & Constraints \\ \hline
1     & 25   & $1 \leq n,k \leq 10$, $k$ divides $n$ \\ \hline
2     & 25   & $1 \leq n,k \leq 10$\\ \hline
3     & 25   & $1 \leq n,k \leq 100\,000$, $k$ divides $n$ \\ \hline
4     & 25   & $1 \leq n,k \leq 100\,000$\\ \hline
\end{tabular}
