\problemname{Web Page}
\illustration{0.4}{flow}{Image taken from \href{https://commons.wikimedia.org/wiki/File:Data\_Flow\_of\_the\_Internet\_Protocol\_Suite.PNG}{commons.wikimedia.org}}

Often there is trouble when Icelandic companies or societies
need to make a web page. These days the URLs can contain
Icelandic letters, but the norm is still to omit them.
Of course all special characters and whitespace needs to
be omitted as well.

Many of the companies who need to do this are not particularly
good with technology, so you see this as an opportunity.
You can offer the service of figuring out a domain name for
them and charge incredible rates.

The first step is to throw out everything in the input
that is not a letter or digit. Next all upper case characters
need to be converted into lower case characters.
All accented characters lose their accent (for example
\texttt{á} becomes \texttt{a}). Finally all other Icelandic
characters need to be changed. The letter \texttt{ö} 
becomes \texttt{o}, \texttt{æ} becomes
\texttt{ae}, \texttt{ð} becomes \texttt{d} and finally
\texttt{þ} becomes \texttt{th}.

\section*{Input}
The input consists of a single line.
This line can contain all printable ASCII characters
along with the characters
\texttt{Á},
\texttt{á},
\texttt{Ð},
\texttt{ð},
\texttt{É},
\texttt{é},
\texttt{Í},
\texttt{í},
\texttt{Ó},
\texttt{ó},
\texttt{Ú},
\texttt{ú},
\texttt{Ý},
\texttt{ý},
\texttt{Þ},
\texttt{þ},
\texttt{Æ},
\texttt{æ},
\texttt{Ö},
\texttt{ö}.
In this list each upper case character is followed by their
lower case equivalent.
However, the only whitespace in the input will be spaces
along with a newline character at the end.
The line will be at most $100$ characters, along with
a newline character.

\section*{Output}
Print the domain name that corresponds to the input,
based on the rules above. Also add \texttt{.is}
at the end, and print it all on one line.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 25   & Only ASCII letters in the input. \\ \hline
2     & 25   & Only ASCII characters in the input. \\ \hline
3     & 50   & No further constraints. \\ \hline
\end{tabular}

