\problemname{Manhattanstíflur}
\illustration{0.3}{gridlock}{Image from \href{https://commons.wikimedia.org/wiki/File:Gridlock.svg}{commons.wikimedia.org}}

As you probably already know, the streets in Manhattan all lay north to south or east to west. Let us number the streets that go from north
to south $0, 1, \dots, n$ where the $0$ is the street furthest west. Let us also number the streets going east to west $0, 1, \dots, m$
where $0$ is the street furthest north. Then we can denote an intersection by the numbers of the streets that make up the intersection,
from $(0, 0)$ to $(n, m)$. We are interested in being able to get from the north-west corner $(0, 0)$ to the south-east corner $(n, m)$ by
travelling along the streets.
The problem is that often sections of road are closed due to construction work or other problems. Can you answer when such closures close
all routes from $(0, 0)$ to $(n, m)$?

\section*{Input}
The first line of input contains a single positive integer $q$. Next there is a line with two positive integers $n, m$, the number of streets
in either direction. Finally there are $q$ lines, each with information about a section of road that gets closed. Each line contains four
integers $x_1, y_1, x_2, y_2$ satisfying $0 \leq x_1, x_2 \leq n$ and $0 \leq y_1, y_2 \leq m$. This means that the section of road from
the intersection $(x_1, y_1)$ to the intersection $(y_1, y_2)$ is being closed. These intersections are always adjacent to one another.

\section*{Output}
If query number $i$ closes all routes from $(0, 0)$ to $(n, m)$, print $i$. If it's still possible to travel from $(0, 0)$ to $(n, m)$ after
all queries, print $-1$ instead.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 10   & $n = 1$, $m, q \leq 500$ \\ \hline
2     & 10   & $n = 2$, $m, q \leq 500$ \\ \hline
3     & 20   & $n, m, q \leq 500$ \\ \hline
4     & 30   & $n, m, q \leq 5\,000$ \\ \hline
5     & 30   & $n, m \leq 10^9$, $q \leq 5 \cdot 10^5$ \\ \hline
\end{tabular}

