\problemname{Liðaskipting 2}
\illustration{0.3}{tables}{Image from \href{https://commons.wikimedia.org/wiki/File:Tables\_gigognes\_STB6985.jpg}{commons.wikimedia.org}}

The competitive programming association of Iceland has been hard at work preparing the contest.
Luckily, the association gets plenty of help from Reykjavík University.
However, this year there was a bit of a problem.
Due to the cyberattack on the university some of the registration data was lost!
\footnote{Did not actually happen, but the cyberattack did!}
Now the association only knows who is registered, but not to which team they belong to.
The university wants to know how many tables are needed,
but this is hard to answer without knowing the number of teams competing.
Each team must have at least one contestant and can have at most three contestants.
Given this information, along with how many are registered to compete,
can you find the minimum and maximum number of teams that could be registered to compete?

\section*{Input}
The first and only line of input contains an integer $n$, the number of registered contestants.

\section*{Output}
Print two lines.
On the first print how many teams could be registered at the most.
On the second print how many teams could be registered at the least.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 24   & $1 \leq n \leq 3$. \\ \hline
2     & 24   & $1 \leq n \leq 30$. \\ \hline
3     & 24   & $1 \leq n \leq 30\,000$. \\ \hline
4     & 24   & $1 \leq n \leq 10^{12}$. \\ \hline
5     & 4    & $1 \leq n \leq 10^{100}$. \\ \hline
\end{tabular}
