\problemname{Leikjahönnun}
\illustration{0.3}{dice}{Image from \href{https://commons.wikimedia.org/wiki/File:Black_Polyhedral_Game_Dice.jpg}{commons.wikimedia.org}}

Gulli is working on a new board game. In the game dice are often rolled to determine what happens next. To have a good idea of how
the game plays he needs to know how likely each possible outcome is for a particular set of dice. Can you help him? All dice in the
input are unbiased, or in other words, all sides are equally likely to be the outcome.

\section*{Input}
The first line of the input contains a single integer $n$, the number of dice. Next there are $n$ lines, each describing a single die.
The first integer on the $i$-th line, $d_i$, describes the number of sides on the die. Then there are $d_i$ integers $x_{i, j}$ separated
by spaces describing the number on the $j$-th side of the $i$-th dice.

\section*{Output}
Print the probabilities of all outcomes when all the dice are rolled and the result is summed up. For each possible outcome $x$ print
\texttt{x p/q} where $p/q$ is a reduced fraction giving the probability that the outcome is $x$. You should only print outcomes with a positive
probability and the outcomes should be printed in ascending order.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $n = 1$, $1 \leq d_i, x_{i, j} \leq 100$ \\ \hline
2     & 30   & $1 \leq n \leq 2$, $1 \leq d_i, x_{i, j} \leq 100$ \\ \hline
3     & 40   & $1 \leq n \leq 7$, $1 \leq d_i \leq 100$, $1 \leq x_{i,j} \leq 500$ \\ \hline
4     & 10   & $1 \leq n \leq 7$, $1 \leq d_i \leq 100$, $1 \leq x_{i,j} \leq 30\,000$\\ \hline
\end{tabular}

