\problemname{Fibs og Dibs}
\illustration{0.3}{numbers}{Picture from \href{https://flickr.com/photos/morebyless/9423385629}{flickr.com}}
As everyone knows, Dagur and Elvar are gamers and love to play long games.
They now want to play their second favourite game Fibs and Dibs.
The game works as follows, first Dagur picks an integer $a$, then Elvar picks another greater or equal integer $b$.
Finally they choose $n$, the number of rounds to play.

In each round Dagur start by calling ``Fibs'', when he does that they add their two numbers
together and Dagur takes the new number, so that $a$ takes the value of $a + b$.
Then Elvar says ``Dibs'' and they repeat the steps, except now Elvar takes the new number, so that $b$ takes the value of $a + b$.

As they are quite impatient, they don't want to play $n$ rounds, since they really want to go play their favourite game
Dibs and Fibs. So they ask you to help them find out which numbers they will end up with after the $n$ rounds.

\section*{Input}
The first line of the input contains two integers, $a$, the number that Dagur picks,
and $b$ the number that Elvar picks, where $1 \leq a \leq b \leq 10^5$.
Then one line follows with one integer $n$, the amount of rounds Dagur and Elvar want to play.

\section*{Output}
Output the two integers that Dagur and Elvar end up with.
Output the numbers in one line sperated by a space, first the integer that Dagur ends with
and then the integer that Elvar ends with. Since the numbers can become quite large,
you should output them modulo $10^9 + 7$.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $0 \leq n \leq 10$ \\ \hline
2     & 40   & $0 \leq n \leq 10^5$ \\ \hline
3     & 40   & $0 \leq n \leq 10^{12}$ \\ \hline
\end{tabular}

