\problemname{Skammstöfun}
\illustration{0.3}{abbreviations}{Photo from \href{https://flickr.com/photos/apelad/15955349666/}{flickr.com}}

Before Hannes founded the startup company which focused on naming startup companies,
a more primitive method of naming was used for companies, services and products.
The entity which was to be named was simply described with words and an abbreviation was formed from the words.

The words were written down and each one started with either a small letter or a capital letter.
Initially, the abbreviation was empty and then the words were processed.
If a word started with a capital letter then it was used as part of the abbreviation, otherwise it was skipped.
When a word was used in an abbreviation, the first letter of the word was taken and added to the back abbreviation.
The abbreviation was therefore made up of the first letter of each word starting with a capital letter, in the same order as the words.

\section*{Input}
Input consist of two lines.
The former line contains a single integer $n$, the number of words.
The latter line consists $n$ words, separated by spaces.
Each word consists entirely of letters in the English alphabet.
The number of symbols in the input is between $1$ and $1\,000$.

\section*{Output}
Output one line containing the abbreviation.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 25     & $n = 1$ \\ \hline
2     & 35     & $1 \leq n \leq 100$, each word starts with a capital letter \\ \hline
3     & 40     & $1 \leq n \leq 100$ \\ \hline
\end{tabular}

