\problemname{Diggy Hole}
\illustration{0.4}{hole}{Image taken from \href{https://gaming.stackexchange.com/questions/14695/how-do-you-fix-massive-holes-that-appear-in-the-ground/14705}{gaming.stackexchange.com}}

There is an old riddle that is as follows:
If four workers take four hours to dig four holes,
how long does it take two workers to dig half a hole?

We see that each worker takes four hours to dig a hole,
so assuming they can work on the same hole in tandem,
the answer should be one hour. The answer to the riddle
is however that there is no such thing as half a hole,
which is a dumb and stupid answer. Absolute cop out.

Thus, we now solve the actual riddle by giving that $n$
workers take $h$ hours to dig out $x$ cubic metres. We
then ask how long it would take $m$ workers to dig out
$y$ cubic metres. You may assume all workers work equally
hard, they continue working at the same pace indefinitely
and that they can work in tandem on the same cubic metres.

\section*{Input}
The input consists of $5$ lines.
The lines contain the integers $n, h, x, m, y$ in that
order. The values are always between $1$ and $100$, inclusive.

\section*{Output}
Print the answer to the updated riddle. As the answer
might not be an integer we will consider an answer correct
if its absolute or relative error from the correct answer
is at most $1\%$. Thus it does not matter how many digits
are printed after the decimal point exactly, as long as it
is accurate enough.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 50   & The answer is an integer. \\ \hline
2     & 50   & No further constraints. \\ \hline
\end{tabular}

