\problemname{ASCII Box 3}
\illustration{0.4}{chair}{Image from \href{https://commons.wikimedia.org/wiki/File:Chair-ascii.png}{wikimedia.commons.org}}

Another programming contest, another problem about ASCII boxes!
So far all the ASCII boxes have been missing something.
The more artistically inclined contestants of the last years have complained
the problems lacked depth, so this year we have to add a third dimension to 
the images.

To draw the box the letters \texttt{+}, \texttt{-}, \texttt{|}, \texttt{/}
and \texttt{x} should be used.
The vertical edges are drawn with \texttt{|} and the horizontal edges with \texttt{-}.
The corners of the box are drawn with \texttt{+} and \texttt{/} is used for edges that
face away from our perspective. Finally \texttt{x} is used if two 
non-parallel edges overlap (on the picture). If a corner and edge overlap it should still
be drawn with a \texttt{+}.

To make sure the box is printed correctly, an appropriate number of spaces has to be placed
before and between the letters of each line.
Additionally, do not print any extra spaces after the last letter of a line, just a single
newline character after the last letter on each line.

The box has some specific height $h \geq 1$, width $w \geq 1$ and depth $d \geq 1$.
The vertical edges are then composed of $2$ \texttt{+} and $(h - 2)$ \texttt{|}, except
if $h = 1$ then it's only a single \texttt{+}.
Similarly the horizontal edge is $2$ \texttt{+} and $(w - 2)$ \texttt{-}, except if
$b = 1$ then it's only a single \texttt{+}.

This lets us draw the front face of the box, which is a $h \times w$ rectangle. If $d > 1$
then $(d - 2)$ \texttt{/} need to be drawn from each corner going up and to the right.
Then the back face of the box needs to be drawn in the same manner as the front one
at the end of the \texttt{/} sequence.

\section*{Input}
The first and only line of input contains three integers $h, w, d$, the dimensions of
the box as described above.

\section*{Output}
Print a box with the given dimensions, as described above.
Note that the output must be exactly correct, even up to whitespace.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $1 \leq h, w, d \leq 3$. \\ \hline
2     & 30   & $2 \leq h, w, d \leq 8$. \\ \hline
3     & 20   & $d = 1, 1 \leq h, w \leq 100$. \\ \hline
4     & 30   & $1 \leq h, w, d \leq 100$. \\ \hline
\end{tabular}
