\problemname{Passport Dates}
\illustration{0.4}{vegabref}{An Icelandic passport.}

Konráð has managed to obtain a big pile of Icelandic passports (don't ask, don't tell
anyone either). Now he has the fun task ahead of him of getting all of the data he wants
from the passports. He constructed a small robot arm to automatically open each one of
them and take pictures of the relevant data. Then he threw together some image processing
code to turn the pictures into the text he wanted from them. This was of course the simple
part, now comes the tough part. Converting the format of the data to the ISO-8601 standard.

He has lots of lines of text from Icelandic passports of the format
\texttt{dd ISM /ENM yy} where \texttt{dd} is the day of the month,
\texttt{ISM} is a three letter abbreviation of a month in Icelandic,
\texttt{ENM} is a three letter abbreviation of a month in English and
\texttt{yy} are the last two digits of the year.
This date says when the passport will expire.

He wants to change this data to the format \texttt{yyyy-mm-dd}
where \texttt{yyyy} is the full year, \texttt{mm} is the month and
\texttt{dd} the day of the month. All these numbers, both here and
above, will have a fixed number of digits, so for example $7$ will
be formatted as \texttt{07}.

All the passports in the input will expire somewhere in the range
$2015$ and $2035$. The date when this contest took place is eighth
of March $2025$.

The Icelandic month name abbreviations are
\texttt{JAN},
\texttt{FEB},
\texttt{MAR},
\texttt{APR},
\texttt{MAÍ},
\texttt{JÚN},
\texttt{JÚL},
\texttt{ÁGÚ},
\texttt{SEP},
\texttt{OKT},
\texttt{NÓV},
\texttt{DES}.

The English month name abbreviations are
\texttt{JAN},
\texttt{FEB},
\texttt{MAR},
\texttt{APR},
\texttt{MAY},
\texttt{JUN},
\texttt{JUL},
\texttt{AUG},
\texttt{SEP},
\texttt{OCT},
\texttt{NOV},
\texttt{DEC}.

\section*{Input}
One line of text from a passport as described above.

\section*{Output}
The date from the passport in ISO-8601 format, as described above.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 10   & All dates are exactly the day today (day of the contest). \\ \hline
2     & 25   & All dates are in this month (month of the contest).\\ \hline
3     & 50   & All dates are in the year $2024$. \\ \hline
4     & 15   & No further constraints. \\ \hline
\end{tabular}

