\problemname{Trapizza}
\illustration{0.5}{Trapizza}{Picture drawn by Eva.}

Tryggvi, the owner of Mahjong Pizza, and Ómar, the owner of Trapizza, are nemeses.
They always run into each other downtown and their conversations always end up in heated arguments, more often than not related to their pizzas.
Tryggvi says that trapezoid shaped pizzas are immoral and society should not allow them to be sold in the country.
Ómar says that round pizzas are a thing of the past and the future is all about having more creative shaped objects.

Their last argument ended up with a comparison of whose pizza was bigger, since the prize of the pizzas are the same.
They cannot figure out which one has the bigger pizza, they are no mathematicians after all, so they are asking for your help.
Tryggvi tells you the diameter of the pizzas he sells and Ómar tells you both sides and height of the pizzas he sells.

\section*{Input}
The input consists of four lines. The first line consists of a single integer $0 \leq d \leq 100$, the diameter of Mahjong's pizza.
The second line consists of a single integer $0 \leq a \leq 100$, the length of one of the parallel sides of Trapizza's pizza.
The third line consists of a single integer $0 \leq b \leq 100$, the length of the other parallel side of Trapizza's pizza.
The fourth line consists of a single integer $0 \leq h \leq 100$, the height of Trapizza's pizza.

\section*{Output}
If Trapizza has the bigger pizza, output \texttt{"Trapizza!"}. 
If Mahjong has the bigger pizza, output \texttt{"Mahjong!"}.
If the pizzas are the same size, output \texttt{"Jafn storar!"}.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 100   & No further constraints. \\ \hline
\end{tabular}
