\problemname{Uh-Oh, It Is Nighttime!}
\illustration{0.4}{nighttime}{Image from Minecraft}

Alex is playing the famous game Minecraft and has been travelling all day trying to find the \emph{perfect biome} for her base.
What she does not realise is that in the time she has travelled, nighttime has arrived.
She only realises once she starts seeing mobs spawning and starts panicking because she has nothing to defend herself with but her bare fists, which is not effective.
She needs to make a temporary base and quick!
Help Alex find the amount of dirt blocks she will need for her temporary base.

The temporary base is a cuboid that is empty on the inside so that Alex can stay protected throughout the night.
All four walls have a thickness of $1$ with the height on the inside as $h-1$.
Since Alex is $2$ blocks tall and $1$ block wide and deep, the
house needs to be at least $3$ blocks in each dimension and the ground is already made of dirt blocks.

\section*{Input}
The first line contains one integer $i$, the total number of side lengths we receive as input.
Then there are $i$ lines, for however many side lengths we receive we get the following in order:
\begin{itemize}
  \item If $i = 1$, we receive only one side that contains one integer $l$, representing the width and the length, in this case the height is always 3.
  \item If $i = 2$, we receive two sides that contain two integers $w$ and $l$, representing the width and the length respectively, in this case the height is always 3.
  \item If $i = 3$, we receive three sides that contain three integers $w$, $l$, and $h$, representing the width, the length, and the height respectively.
\end{itemize}

\section*{Output}
The total number of dirt blocks Alex will need to survive the night.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Groups & Points & Constraints \\ \hline
1     & 10 & The input corresponds to a $3 \times 3$ house with minimal height.  \\ \hline
2     & 20 & $i = 1$, and $3 \leq l \leq 100$\\ \hline
3     & 30 & $i = 2$, and $3 \leq w,l \leq 100$ \\ \hline
4     & 40 & $i = 3$, and $3 \leq w,l,h \leq 100$ \\ \hline
\end{tabular}
