\problemname{Guest List}
\illustration{0.4}{guestlist}{Image taken from \href{https://commons.wikimedia.org/wiki/File:Guest\_list\_of\_people\_attending\_Ulysses\_S.\_Grant\%27s\_funeral,\_August\_8,\_1885\_-\_DPLA\_-\_5076ade4d3accf58b0810e7c8483b4d1\_(page\_1).jpg}{commons.wikimedia.org}}

A new hotel has implemented strict entry rules, allowing access only to those on a special guest list. Due to high demand and technical issues with maintaining the list on paper, a command-line program is needed to register, remove, and check names on the list.

\section*{Input}
\begin{itemize}
    \item The first line contains the positive integer $N$, representing the number of commands that follow.
    \item The next $N$ lines contain commands of the following types:
    \begin{itemize}
        \item \texttt{+ name} – Adds a name to the guest list.
        \item \texttt{- name} – Removes a name from the guest list.
        \item \texttt{? name} – Checks whether a name is on the guest list.
    \end{itemize}
\end{itemize}

Names only include the English lowercase letters \texttt{a} to \texttt{z} and names are at most
$8$ characters in length. A name that's already on the list will never be added again, and no
name will be removed that's not on the list.

\section*{Output}
For each \texttt{? name} command, the program should print \texttt{Jebb} if the name is on the list, otherwise \texttt{Neibb}.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Score & Constraints \\ \hline
1     & 20   & Only \texttt{? name} commands and $N \leq 20$. \\ \hline
2     & 50   & $N \leq 1\,000$. \\ \hline
3     & 30   & $N \leq 200\,000$. \\ \hline
\end{tabular}
