\problemname{Homework Workload}
\illustration{0.4}{homework}{Image taken from \href{https://www.publicdomainpictures.net/en/view-image.php?image=132819\&picture=science-homework}{publicdomainpictures.net}}

Some years ago the principal of Menntaskólinn á Akureyri
said some things at a speech that did not go over so well
with students. He claimed that if students would just stay
after school for a single hour each weekday there would be
no homework to do at home afterwards and that complaints
about homework were overblown.

Students that have attended, or are attending, Menntaskólinn
á Akureyri (or other Icelandic high schools for that matter)
are quite aware that this is utter hogwash. Anyone who has
had to survive the Íslandsáfangar at Menntaskólinn á Akureyri
knows it especially well. To show how off the mark this is,
some data has been collected about assignments and deadlines.
Here we will then investigate one has to study after school
per day to finish everything.

Icelandic sagas, atom poets, learning the names of waterfalls
and whale species, and you better remember the name of
the teacher's favourite pool to get the bonus question right!
Utter lunacy, I could keep going all day long! 
It should all be done away with immediately and everything-

What? No I haven't finished the problem description yet.
Hey! No- I am not done! Let the keyboard alo-

Sorry for that.

Each assignment is assigned on some particular day
and has to be finished at the latest on some particular day.
Additionally each problem takes some number of time units
to finish. If you intend to always work $x$ time units per day
(unless you already finished all your homework), what does
$x$ need to be at minimum to make sure you can finish
all the assignments in time?

\section*{Input}
The first line of input contains a single integer $n$,
the number of assignments. It will always hold that
$0 \leq n \leq 100\,000$.
Next there are $n$ lines where the $i$-th line contains
the details of the $i$-th assignment.

Each such line contains three integers $a_i, b_i, t_i$ where
$a_i$ is the day the assignment is assigned, $b_i$ is the
day it is due (the assignment can be turned in at the end
of that day) and $t_i$ is the number of time units it takes
to finish the assignment. It will always hold that 
$0 \leq a_i, b_i, t_i \leq 10^9$ and $a_i \leq b_i$.

Note that the values in the input are large and computations may not fit in $32$ bits.

\section*{Output}
Print how many time units you have to work per day
at a minimum to finish all assignments in time.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 15   & $n = 1$. \\ \hline
2     & 20   & $n \leq 100$ and $t_i \leq 100$ for all $i$. \\ \hline
3     & 25   & $a_i = b_i$ for all $i$. \\ \hline
4     & 40   & No further constraints. \\ \hline
\end{tabular}

