\problemname{Steam Column}
\illustration{0.4}{strokur}{Image by Patricia Fehrentz}

Often there is steam rising from the ground around Krafla.
Depending on the wind at any given time the column of steam
can be leaning in different directions. Plenty of useful data
can be inferred from researching such steam columns.

A research team has now taken two pictures where the
steam column is leaning two different ways. By how many
degrees has the wind direction changed at a minimum?

The direction of the steam column is given as degrees
from north, so north is $0^{\circ}$, west is
$90^{\circ}$, south is $180^{\circ}$ and east is
$270^{\circ}$. One degree east of north is then
$359^{\circ}$.

For example, if the pictures show angles of $170^{\circ}$ and 
$100^{\circ}$ the answer is $70^{\circ}$, because the
steam column can rotate in either direction. If the
pictures show angles of $355^{\circ}$ and
$7^{\circ}$ the answer is $12^{\circ}$ because 
$359^{\circ}$ and $0^{\circ}$ are adjacent.

\section*{Input}
The input consists of two lines.
The first line contains the direction of the steam
column on the first picture, given as an integer from
$0$ to $359$.
The second line contains the direction of the steam
column on the second picture, given as an integer from
$0$ to $359$.

\section*{Output}
Print the minimum possible number of degrees the steam column
has rotated between taking the pictures.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 100   & No further constraints. \\ \hline
\end{tabular}

