\problemname{Framvindustika}
\illustration{0.3}{estimation}{Image from \href{https://xkcd.com/612}{xkcd.com}}

Erla works at a software company that has recently received complaints from users.
The users are unhappy with a specific operation in the software which has a long runtime.
The users are uncertain whether the program is frozen or active after starting the operation.
The code for the operation was a prototype which was only meant to be used for a presentation within the company.
When Erla's superiors saw the prototype they decided to ship the feature in the next version.

Erla suggests reviewing the implementation of the operation and researching whether an optimized version can be written in its stead.
She is certain that this is possible, but it might be time consuming.
Erla's direct superior decides to conduct a survey regarding user interface and user experience to determine the next course of action.

After a month of surveying, the result is in.
When a project takes a long time it helps the mental state of a person to experience that some milestones are being met.
The same applies to users which are waiting for the computer to finish running heavy computations.
Based on the results of the survey, a decision is made to add a progress bar to indicate to the user that the computation is ongoing and to give the user a feeling for how long until the operation finishes.

Erla disagrees profusely with the decision and would rather focus on improving the efficiency of the operation.
She still has to finish implementing the progress bar today.
She asks for your help, can you implement the progress bar for Erla so she can dive deep into research?


\section*{Input}
Input consists of a single line containing two integers $p$, where $0 \leq p \leq 100$, representing the percentage of the operation which is finished, and $w$, the width of the progress bar.

\section*{Output}
Print the current state of the progress bar.
The progress bar should be output in a single line and starts with the symbol \texttt{\lbrack}, then $w$ symbols, where the first $p$ percent of them are \texttt{\#} and the rest are \texttt{-}, then \texttt{\rbrack} follows.
Next comes a space, the symbol \texttt{\textbar}, then another space and finally the percentage shall be written next to the progress bar.
The percentage shall be written right justified with columns for four symbols.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 10     & $w = 100$ \\ \hline
2     & 10     & $w = 10$ \\ \hline
3     & 50     & $1 \leq w \leq 1\,000$ \\ \hline
4     & 30     & $1 \leq w \leq 10^6$ \\ \hline
\end{tabular}
