\problemname{Cards Sorting}
\illustration{0.4}{impact}{Image taken from \href{https://commons.wikimedia.org/wiki/File:Japan\_Impact\_2023\_-\_Yu-Gi-Oh\_(52765156950).jpg}{commons.wikimedia.org}}

Atli owns a terrible amount of cards and sometimes he
has trouble keeping them all organised. Thus he was thinking
it might be good to create a digital database to keep track
of it all.

The database has to offer different ways to sort the cards.
To do this we should first consider the information that
each card has.

Each card has a name, for example ``Bláeygður Hvítur Dreki''
or ``Dimmur Seiðkarl''. The names always contain only English
letters along with spaces, and have length at most $32$.
The names do not start or end with spaces and are not empty.
Each card also has a $8$ digit ID number, for example 
55144522. No two different cards have the same ID\@. 
Each card also has a type and possibly a subtype. We
give the types and subtypes in the order they should be
sorted here below, they are

\begin{itemize}
    \item \texttt{Skrimsli}
    \begin{itemize}
        \item \texttt{Venjulegt}
        \item \texttt{Ahrifa}
        \item \texttt{Bodunar}
        \item \texttt{Samruna}
        \item \texttt{Samstillt}
        \item \texttt{Thaeo}
        \item \texttt{Penduls}
        \item \texttt{Tengis}
    \end{itemize}
    \item \texttt{Galdur}
    \begin{itemize}
        \item \texttt{Venjulegur}
        \item \texttt{Bunadar}
        \item \texttt{Svida}
        \item \texttt{Samfelldur}
        \item \texttt{Bodunar}
        \item \texttt{Hradur}
    \end{itemize}
    \item \texttt{Gildra}
    \begin{itemize}
        \item \texttt{Venjuleg}
        \item \texttt{Samfelld}
        \item \texttt{Mot}
    \end{itemize}
    \item \texttt{Annad}
\end{itemize}

This means \texttt{Skrimsli} has the subtype \texttt{Thaeo}, 
which comes before the subtype \texttt{Tengis} and so on.
Furthermore \texttt{Gildra} comes after \texttt{Galdur} no
matter what subtype it is. \texttt{Annad} has no subtype.

Finally each card has a release date, given in the format
\texttt{yyyy-mm-dd} which gives the year, month and day
in the \texttt{ISO-8601} format.

\section*{Input}
The input starts with a line containing a single positive
integer $1 \leq n \leq 1\,000$.
Next there are $n$ lines, each with one card.
That line contains the name, ID, type and release date
of the card, separated by commas. If the type has a subtype
it is given in the format \texttt{type {-} subtype}.

Finally there is a line with the words \texttt{nafn},
\texttt{id}, \texttt{flokkur} and \texttt{dagsetning}
separated by spaces in some order. The cards should be
sorted first by the first item on the line, then ties 
broken by the second item and so on. Here \texttt{nafn}
means name, \texttt{id} is ID, \texttt{flokkur} is type
and \texttt{dagsetning} is date.

Names are sorted alphabetically, IDs by ascending value,
types in the order given above and dates in ascending 
chronological order. Here alphabetical order means by
ASCII value, so spaces are first, then upper case letters
and then lower case letters. This is the default order
for strings in most programming languages.

\section*{Output}
After the cards have been sorted into the right order,
print the name of each card, in that order. Print one
card name per line.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 5   & $n = 1$. \\ \hline
2     & 10   & Cards are sorted by names first. \\ \hline
3     & 15   & Cards are sorted by ID first. \\ \hline
4     & 20   & Cards are sorted by type first, then ID\@. \\ \hline
5     & 20   & Cards are sorted by date first, then type, then name. \\ \hline
6     & 30   & No further constraints. \\ \hline
\end{tabular}

