\problemname{Prjónamynstur}
\illustration{0.3}{knitting}{Photo from \href{https://www.flickr.com/photos/30478819@N08/50598685068}{flickr.com}}

Heiðrún thoroughly enjoys knitting all sorts of garments for her family members.
Whenever a new baby arrives in the family, one can expect that a dress, hat or sweater is her next project.

When Heiðrún knits, she often makes use of recipes, also known as knitting patterns, which can be found in books, magazines or even on the internet.
These recipes are displayed in a graphic manner as tiles in a two dimensional grid.
There are many different types of knitting loops which affect the appearance of the clothing.
Therefore, each tile in the recipe is marked with a symbol to indicate what type of loop should be knitted.
Since the types of loops are different, knitting them requires varying amounts of yarn.
The amount of yarn used is measured in millimeters and the costs of each type of loop are the following:

\begin{tabular}{|l|l|l|}
    \hline
    Type of loop                        & Symbol                  & Yarn in millimeters \\ \hline
    Garter stitch & \texttt{.}              & $20$ \\ \hline
    Yarn over                           & \texttt{O}              & $10$ \\ \hline
    Slip one stitch, knit next stitch and pass slip stitch over knit stitch & \texttt{\textbackslash} & $25$ \\ \hline
    Knit two stitches together & \texttt{/}              & $25$ \\ \hline
    Knit three stitches together & \texttt{A}              & $35$ \\ \hline
    No stitch                            & \texttt{\^{}}           & $5$  \\ \hline
    Purl on right side, knit on wrong side & \texttt{v}              & $22$ \\ \hline
\end{tabular}

Now Heiðrún is wondering whether she has enough yarn for her next project.
If she shows you the recipe she intends to follow, can you tell her how much yarn she will need?

\section*{Input}
The first line of input consists of two integers $n$, the number of rows in the recipe, and $m$, the number of columns in the recipe.
Then $n$ lines follow, each consisting of $m$ symbols, where each line represents a row in the recipe.
You may assume the recipe will only contain symbols from the table above.

\section*{Output}
Output one integer, the amount of yarn required for the recipe in millimeters.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 40     & $1 \leq n, m \leq 50$ \\ \hline
2     & 40     & $1 \leq n, m \leq 1\,000$ and the recipe consists entirely of garter stitches. \\ \hline
3     & 20     & $1 \leq n, m \leq 1\,000$ \\ \hline
\end{tabular}

