\problemname{EIEIO}
\illustration{0.4}{fjarrekstur}{Image by Jóna Þórunn Ragnarsdóttir, taken from \href{https://commons.wikimedia.org/wiki/File:Fjarrekstur\_vid\_Gaukshofda.JPG}{commons.wikimedia.org}}

Jörmunrekur has grown tired of all these programming problems.
To avoid the digital world he has decided to move into
the countryside and become a farmer.

Naturally he had some trouble when he was separating the
sheep for the first time. He was trying to count how many
sheep were already separated, but because the other
people present were wearing wool outfits he ended up counting
them as well. Then just as he finished counting he slipped
in the mud and ended up laying flat on the ground. It wasn't
all bad he thought though, as from this angle he had the idea
of counting all the legs he could see. Using these two counts
he figured he could find the answer.

\section*{Input}
The input consists of two lines. The first line contains
a single integer $n$, the number of sheep and people in total,
not including Jörmunrekur.
The second line contains a single integer $m$, the number of
legs Jörmunrekur counted. He did not count his own legs.
No creature present is missing any limbs. If Jörmunrekur saw
a sheep or person he saw all their legs.

\section*{Output}
Print the number of sheep Jörmunrekur counted. 
If there is no chance Jörmunrekur counted correctly, 
instead print ``Rong talning''.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 100   & $0 \leq n, m \leq 1\,000$ \\ \hline
\end{tabular}

