\problemname{Save the Planets}
\illustration{0.4}{balatro}{Image taken from \href{https://commons.wikimedia.org/wiki/File:The\_Fool\_and\_the\_Lady\_Fool.jpg}{commons.wikimedia.org/}}

Balatro is a game that has attracted many, not least of whom is Elvar.
Elvar loves to play Balatro and is now in the middle of a game which has a good chance of
beating his high score. The goal of Balatro is beating blinds by playing poker hands to get
to a target score $x$. All poker hands have different numbers of chips and multipliers.
The total score for a poker hand is then calculated as \texttt{chips} $\cdot$ \texttt{multiplier}.
For example if you have $50$ chips and multiplier $4$ you get $200$ points for that hand.
After each blind you can then buy jokers, tarot cards and planet cards to make your poker
hands stronger, with the goal of scoring more points.

This game Elvar is playing with a special deck called \emph{plasma deck}. When playing with this
deck, instead of multiplying chips and the multiplier, you first average them and then
multiply. For example if you have $50$ chips and multiplier $4$ like before, they are first
averaged. Then you have $27$ chips and multiplier $27$, making your score $729$.

Elvar has been quite lucky in this Balatro game and managed to fetch the good old
\href{https://balatrogame.fandom.com/wiki/Perkeo}{\emph{Perkeo}} early in the game.
Thus he has decided he will try to collect copies of the planet card 
\href{https://balatrogame.fandom.com/wiki/Planet\_Cards}{\emph{Neptune}} with the intent
of finding \href{https://balatrogame.fandom.com/wiki/Vouchers}{\emph{Observatory}}.
Elvar has managed to arrange his deck such that he always manages to play a \emph{Royal flush}
which gives him $151$ chips and a multiplier of $8$. He also knows that if he uses a
\emph{Neptune} card he adds $40$ chips and a multiplier of $4$ to that. For example if
he uses two \emph{Neptune} cards, a \emph{royal flush} gets him $231$ chips and a multiplier
of $16$, which after accounting for the \emph{plasma deck} nets $123.5$ chips and a multiplier
of $123.5$.

But now Elvar is in a bit of a pickle. He was so sure he would find the \emph{Observatory}
after the last blind that he sold all his jokers. But unfortunately the \emph{Observatory}
was nowhere to be found.
Saddened by this he tried to make the best of a bad situation and bought the joker
\href{https://balatrogame.fandom.com/wiki/Constellation}{\emph{Constellation}}.
What makes this joker good is that after each hand, before the score is counted, this joker
multiplies the multiplier by $1 + 0.1 \cdot$ \texttt{number of planet cards used}. So if Elvar
uses $10$ \emph{Neptune} cards, he gets $551$ chips and a multiplier of $96$, which when accounting
for the \emph{plasma deck} becomes $323.5$ chips and a multiplier of $323.5$, which gives
a score of $104,652.25$. Since Elvar is still in a bit of a shock from not finding the
\emph{Observatory} he doesn't know how many cards he needs to use. Can you help him figure
out the minimum number of planet cards he needs to use to win the blind?

\section*{Input}
The input contains a single positive integer $x$, the number of points Elvar has to score
to win the blind.

\section*{Output}
Print the smallest number of planet cards Elvar has to use to win the blind.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 30   & $0 \leq x \leq 6320$ \\ \hline
2     & 30   & $0 \leq x \leq 10^{24}$ \\ \hline
3     & 40   & $0 \leq x \leq 10^{64}$ \\ \hline
\end{tabular}

