\problemname{Contrarianism}
\illustration{0.4}{argument}{Image by Randall Munroe, taken from \href{https://xkcd.com/1432/}{xkcd.com}}

Writing problems for the Icelandic High School Programming Contest is a time
consuming endeavour. Part of the reason for this is how much the judges like
to argue and disagree with each other at meetings. By far the worst
culprit in these matters is Atli, who seems to disagree with absolutely
everything just for the sake of argument. It does not matter what is said,
Atli always says something else.

To save time you could perhaps implement an artificial intelligence that
takes over this self-proclaimed role! Only thing it needs to do is say anything other than
what is in the input!

\section*{Input}
The input consists of a single line.
The input contains up to 10 characters, along with a terminating newline
character.
These characters can be any letters or digits in ASCII, along with spaces.
This can then be all English letters from \texttt{a} to \texttt{z}, all
English letters from \texttt{A} to \texttt{Z}, the digits \texttt{0}
through \texttt{9} and spaces.

Note that the input can be an empty line!

\section*{Output}
Print anything other than the input. The output can be at most $10$ letters
along with a newline character, and is subject to the same character
restrictions as the input. The output must end with a newline character.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 100   & No further constraints. \\ \hline
\end{tabular}

