\problemname{Tölvuíhlutir}
\illustration{0.4}{dwave}{Image from \href{https://commons.wikimedia.org/wiki/File:A\_Wafer\_of\_the\_Latest\_D-Wave\_Quantum\_Computers\_(39188583425).jpg}{commons.wikimedia.org}}

Magni is purchasing a new desktop computer, which raises the important question of which components to buy to put into it. He of course doesn't
have infinite money, so the tricky thing is to get the best possible performance for the money he can spend. In the real world different 
components of course perform differently well at different tasks, but to simplify we will consider only the average performance of any given
component. If he buys a very expensive and nice graphics card, but then a very poor CPU the graphics card will be bottlenecked by the poor
CPU. Thus the computer is only as good as its weakest component. Can you help Magni purchase the best computer he can?

\section*{Input}
The first line contains three positive integers $n, k$ and $p$, where $n$ is the number of available components, 
$k$ is the number of types of different components and $p$ is the amount of money Magni can spend on the computer. 
It is guaranteed that $1 \leq k \leq n$.
The next line contains $k$ strings, each
giving the name of a type of component, separated by spaces. The next $n$ lines will each describe one available component. Each such
line has a string $s$ and two integers $v, g$. The string describes the type of the component and is always one of the $k$ types given
above in the input. The value $v$ gives the price of the component and satisfies $0 \leq v \leq 10^9$. Finally $g$ describes the performance of
the component and satisfies $0 \leq g \leq 10^9$. The computer must contain exactly one component of each type and the performance of
the computer is the minimum of the performance values of its $k$ components.

All strings in the input are at most $10$ letters and contain only English lower and upper case characters. The total length of all
strings in the input is at most $6 \cdot 10^5$.

\section*{Output}
Print the best achievable performance Magni can attain for the money he has. If the money is not enough to build any computer, then instead
print \texttt{O nei!}.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $1 \leq n \leq 1\,000$, no two components are of the same type \\ \hline
2     & 20   & $1 \leq n \leq 1\,000$, the performance of any component is at most $100\,000$ \\ \hline
3     & 20   & $1 \leq n \leq 1\,000$, $k = 1$ \\ \hline
4     & 20   & $1 \leq n \leq 1\,000$ \\ \hline
5     & 20   & $1 \leq n \leq 100\,000$ \\ \hline
\end{tabular}

