\problemname{Tónlistarlisti}
\illustration{0.3}{note}{}

Atli is very disorganized and only has one playlist of songs to listen to. All
songs he likes go into the top of the list, and when he listens to music he starts
with the top song and listens to them in order. If he has listened to them all, he starts
anew from the top.

For some reason the program he uses to listen to music cannot show him how often
he has listened to each song. Thus he asks you to make a program that can maintain
such statistics. He only counts times when he listens to a song from start to end
without interruption.

\section*{Input}
The first line in the input contains one integer $q$, the number of queries.

Next there are $q$ lines, each with one query. They start with a single letter
that denotes the type of query. If the line starts with a $P$ a positive integer $\leq 10^9$
follows, the number of seconds Atli listened to music for. Atli always starts at the top of the list 
and pauses when the time is up. If the line starts with an $L$, a
string with a song name follows, and then the length of that song in seconds. This means Atli
added this song to the top of his playlist, or deleted it from the playlist if it was already present.
If the line starts with $Q$ a song name will follow and the program should print how often Atli has
listened to that song. The song names only contain lower
case English letters and underscores. The total length of all song names in the input is at most
$2 \cdot 10^6$. The playlist is empty at the start and Atli will never listen to music while the playlist
is empty. No two different songs have the same name.

\section*{Output}
For each query that starts with a $Q$, print how often Atli has listened to the corresponding song.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20   & $1 \leq q \leq 1\,000$, songs are never removed from the playlist, each song has length $1$ \\ \hline
2     & 20   & $1 \leq q \leq 1\,000$, songs are never removed from the playlist \\ \hline
3     & 30   & $1 \leq q \leq 5 \cdot 10^5$, songs are never removed from the playlist \\ \hline
4     & 30   & $1 \leq q \leq 5 \cdot 10^5$ \\ \hline
\end{tabular}

