\problemname{Type Faster}
\illustration{0.4}{top20}{Image taken from \href{https://2024.nwerc.eu/main/scoreboard/}{2024.nwerc.eu}}

In programming contests it is often useful to type fast,
especially when time penalties can swing you up and down
many places in the scoreboard. You now wonder how much it
would have taken to win a previous contest.

You are quite optimistic so you assume you will solve all
problems first try, so you only get time penalties for your
first submission in each problem. The best team of the contest
solved every problem, so you need to do the same and beat
their time penalty. Let us also assume the contest has no
time limit, outside of having to beat the top team's time
penalty. It is not sufficient to match their time penalty,
yours has to be strictly lower.

If you turn in a solution at minute $x$, the value $x$ is
added to your time penalty. This means that a solution 
submitted at $1$ minute and $59$ seconds gets a time
penalty of $1$ but one after $2$ minutes gets a time
penalty of $2$.

Thus if you can write $20$ words per minute and a solution
takes $100$ words, and you start by solving that problem,
you will get a time penalty of $5$. But if it were $99$ words
you would get a time penalty of $4$.

You have figured out the solution to every problem in your
head and know exactly how many words each problem would be.
But you are unsure if you can type fast enough to beat the
top team. Thus the question is, how many words per minute do
you need to type to beat the top team?

\section*{Input}
The first line of input contains two integers $n, T$.
$n$ is the number of problems on the contest you have to
solve and $T$ is the time penalty of the top team that you
have to beat. It will always hold that 
$1 \leq n \leq 100\,000$ and $1 \leq T \leq 10^{18}$.
The second and last line of input contains $n$ integers
$w_1, w_2, \dots, w_n$. $w_i$ is the number of words the
solution to the $i$-th problem has. It will always hold that
$0 \leq w_i \leq 10^9$ for all $i$.
The sum of all $w_i$ will not be $0$.

\section*{Output}
Print the lowest number of words per minute needed to
beat the top team.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 10   & $n = 1$. \\ \hline
2     & 15   & $T = 1$. \\ \hline
3     & 25   & $n \leq 100, \sum_{i=0}^n w_i \leq 1\,000$ \\ \hline
4     & 50   & No further constraints. \\ \hline
\end{tabular}

